---
title: "Model Planning and Building"
author: Albert Swingler
output: html_notebook
---

For this phase of the project I want use the the data I scraped from Pew Research Centers website that has the immigration information of congresspeople in the House and the Senate.
One question I want to answer is weather there is a corelation between a congressperson being a immigrant and their party and how they vote on bills.

115th:
https://www.pewresearch.org/fact-tank/2018/08/21/immigrants-or-children-of-immigrants-make-up-at-least-12-of-congress/

116th:
https://www.pewresearch.org/fact-tank/2019/01/24/in-116th-congress-at-least-13-of-lawmakers-are-immigrants-or-the-children-of-immigrants/


Here I imported the data from the tables on the two websites and created two tibbles with it.
```{r}
library("tidyverse")
library("rvest")
library("dplyr")
library("knitr")
library("caret")

purl("deliverable1.Rmd", output = "part1.r") # produces r source from rmd
source("part1.r") # executes the source


congress115 <- read_html("https://www.pewresearch.org/fact-tank/2018/08/21/immigrants-or-children-of-immigrants-make-up-at-least-12-of-congress/")
congress116 <- read_html("https://www.pewresearch.org/fact-tank/2019/01/24/in-116th-congress-at-least-13-of-lawmakers-are-immigrants-or-the-children-of-immigrants/")



names115 <- congress115 %>% html_nodes("tr > td:nth-child(1)") %>% html_text()

generation115 <- congress115 %>% html_nodes("tr > td:nth-child(2)") %>% html_text()

birthplace115 <- congress115 %>% html_nodes("tr > td:nth-child(3)") %>% html_text()

office115 <- congress115 %>% html_nodes("tr > td:nth-child(4)") %>% html_text()

party115 <- congress115 %>% html_nodes("tr > td:nth-child(5)") %>% html_text()

states115 <- congress115 %>% html_nodes("tr > td:nth-child(6)") %>% html_text()

c115Tibble <- tibble(Name = names115, generation = generation115, Parent_or_Members_birthplace = birthplace115, Chamber = office115, Party = party115, State = states115)



names116 <- congress116 %>% html_nodes("tr > td:nth-child(1)") %>% html_text()

generation116 <- congress116 %>% html_nodes("tr > td:nth-child(2)") %>% html_text()

birthplace116 <- congress116 %>% html_nodes("tr > td:nth-child(3)") %>% html_text()

office116 <- congress116 %>% html_nodes("tr > td:nth-child(5)") %>% html_text()

party116 <- congress116 %>% html_nodes("tr > td:nth-child(4)") %>% html_text()

states116 <- congress116 %>% html_nodes("tr > td:nth-child(6)") %>% html_text()

c116Tibble <- tibble(Name = names116, generation = generation116, Parent_or_Members_birthplace = birthplace116, Chamber = office116, Party = party116, State = states116)


```


Cleaning data:
```{r}
c115Tibble$Party <- substr(c115Tibble$Party, 0, 1)
c116Tibble$Party <- substr(c116Tibble$Party, 0, 1)


c115Tibble <- mutate_if(c115Tibble,
is.character, str_replace_all, pattern = "First", replacement = "1")

c115Tibble <- mutate_if(c115Tibble,
is.character, str_replace_all, pattern = "Second", replacement = "2")


as.numeric(as.character(c115Tibble$generation))




c116Tibble <- mutate_if(c116Tibble,
is.character, str_replace_all, pattern = "Immigrant", replacement = "1")

c116Tibble <- mutate_if(c116Tibble,
is.character, str_replace_all, pattern = "Child", replacement = "2")


as.numeric(as.character(c116Tibble$generation))



c115Tibble <- mutate_if(c115Tibble,
is.character, str_replace_all, pattern = "Representative", replacement = "house")

c115Tibble <- mutate_if(c115Tibble,
is.character, str_replace_all, pattern = "Senator", replacement = "senate")

c116Tibble <- mutate_if(c116Tibble,
is.character, str_replace_all, pattern = "Representative", replacement = "house")

c116Tibble <- mutate_if(c116Tibble,
is.character, str_replace_all, pattern = "Senator", replacement = "senate")
```
Relaced the full word for the persons party with just the first letter to match existing data.

Making the persons generation a number instead of first/second and child/immigrant.

Everyone who is not a first or 2nd generation immigrant was given the generation number 3 because I do not have data for how many generations non recently immigrated congresspeople have been Americans.

Switch "Representative" to "house" and "Senator" to "senate" to match existing data.

Setting the generation in the politician tibble to the correct values. Ended up doing this manually after spending days trying to figure out a better way to do this.
```{r}
politition_with_generation <- merge(c115Tibble, c116Tibble)

#changing the name column so its the same as the other data frames so I can merge the generation numbers into those tables
politition_with_generation$Name <- gsub("\\,.*","", politition_with_generation$Name)
colnames(politition_with_generation)[colnames(politition_with_generation) == "Name"] <- "last_name"

#replacing the generation number in politician with the number from politition_with_generation
politician[4,"generation"]=2
politician[5,"generation"]=2
politician[6,"generation"]=2

politician[128,"generation"]=2
politician[129,"generation"]=2
politician[130,"generation"]=2

politician[1436,"generation"]=2
politician[1437,"generation"]=2
politician[1438,"generation"]=2

politician[95,"generation"]=2
politician[96,"generation"]=2
politician[96,"generation"]=2

politician[1439,"generation"]=2
politician[1440,"generation"]=2
politician[1441,"generation"]=2

politician[116,"generation"]=2
politician[117,"generation"]=2
politician[118,"generation"]=2

politician[47,"generation"]=2
politician[48,"generation"]=2
politician[49,"generation"]=2


politician[275,"generation"]=1
politician[276,"generation"]=1
politician[277,"generation"]=1

politician[248,"generation"]=2
politician[249,"generation"]=2
politician[250,"generation"]=2

politician[223,"generation"]=2
politician[224,"generation"]=2
politician[225,"generation"]=2

politician[204,"generation"]=2
politician[205,"generation"]=2
politician[206,"generation"]=2

politician[269,"generation"]=2
politician[270,"generation"]=2
politician[271,"generation"]=2

politician[1486,"generation"]=2
politician[1487,"generation"]=2
politician[1488,"generation"]=2

politician[198,"generation"]=2
politician[199,"generation"]=2
politician[200,"generation"]=2

politician[309,"generation"]=2
politician[310,"generation"]=2
politician[311,"generation"]=2

politician[323,"generation"]=2
politician[324,"generation"]=2
politician[325,"generation"]=2

politician[1500,"generation"]=2
politician[1501,"generation"]=2
politician[1502,"generation"]=2

politician[1492,"generation"]=2
politician[1493,"generation"]=2
politician[1494,"generation"]=2

politician[378,"generation"]=2
politician[379,"generation"]=2
politician[380,"generation"]=2

politician[391,"generation"]=1
politician[392,"generation"]=1
politician[393,"generation"]=1

politician[484,"generation"]=2
politician[485,"generation"]=2
politician[486,"generation"]=2

politician[510,"generation"]=2
politician[511,"generation"]=2
politician[512,"generation"]=2

politician[452,"generation"]=2
politician[453,"generation"]=2
politician[454,"generation"]=2

politician[1546,"generation"]=2
politician[1547,"generation"]=2
politician[1548,"generation"]=2

politician[548,"generation"]=2
politician[549,"generation"]=2
politician[550,"generation"]=2

politician[1538,"generation"]=2
politician[1539,"generation"]=2
politician[1540,"generation"]=2

politician[1535,"generation"]=1
politician[1536,"generation"]=1
politician[1537,"generation"]=1

politician[530,"generation"]=2
politician[531,"generation"]=2
politician[532,"generation"]=2

politician[641,"generation"]=1
politician[642,"generation"]=1
politician[643,"generation"]=1

politician[699,"generation"]=2
politician[700,"generation"]=2
politician[701,"generation"]=2

politician[682,"generation"]=2
politician[683,"generation"]=2
politician[684,"generation"]=2

politician[704,"generation"]=1
politician[705,"generation"]=1
politician[706,"generation"]=1

politician[781,"generation"]=1
politician[782,"generation"]=1
politician[783,"generation"]=1

politician[773,"generation"]=2
politician[774,"generation"]=2
politician[775,"generation"]=2

politician[1600,"generation"]=2
politician[1601,"generation"]=2
politician[1602,"generation"]=2

politician[869,"generation"]=2
politician[870,"generation"]=2
politician[871,"generation"]=2

politician[1612,"generation"]=1
politician[1613,"generation"]=1
politician[1614,"generation"]=1

politician[927,"generation"]=2
politician[928,"generation"]=2
politician[929,"generation"]=2

politician[1630,"generation"]=2
politician[1631,"generation"]=2
politician[1632,"generation"]=2

politician[1645,"generation"]=2
politician[1646,"generation"]=2
politician[1647,"generation"]=2

politician[1648,"generation"]=2
politician[1649,"generation"]=2
politician[1650,"generation"]=2

politician[1083,"generation"]=1
politician[1084,"generation"]=1
politician[1085,"generation"]=1

politician[1159,"generation"]=2
politician[1160,"generation"]=2
politician[1161,"generation"]=2

politician[1658,"generation"]=2
politician[1659,"generation"]=2
politician[1660,"generation"]=2

politician[1148,"generation"]=2
politician[1149,"generation"]=2
politician[1150,"generation"]=2

politician[1680,"generation"]=2
politician[1681,"generation"]=2
politician[1682,"generation"]=2

politician[1165,"generation"]=1
politician[1166,"generation"]=1
politician[1167,"generation"]=1

politician[1176,"generation"]=2
politician[1177,"generation"]=2
politician[1178,"generation"]=2

politician[1219,"generation"]=2
politician[1220,"generation"]=2
politician[1221,"generation"]=2

politician[1696,"generation"]=2
politician[1697,"generation"]=2
politician[1698,"generation"]=2

politician[1278,"generation"]=1
politician[1279,"generation"]=1
politician[1280,"generation"]=1

politician[1312,"generation"]=2
politician[1313,"generation"]=2
politician[1314,"generation"]=2

politician[1717,"generation"]=2
politician[1718,"generation"]=2
politician[1719,"generation"]=2


summary(politician)
```

Graphing
```{r}
averages <- add_column(averages, politician$generation)
colnames(averages)[colnames(averages) == "politician$generation"] <- "generation"


averages$generation <- as.factor(averages$generation)

avg_pct_vote_by_gen <- ggplot(averages, aes(x=generation, y=agree_pct)) + stat_summary(fun.y="mean", geom="bar", color="green") + ylab("agree percentage") +ggtitle("politician generation vs. agree percentage")
avg_pct_vote_by_gen
```

Here we can see that first generation congresspeople - those who immigrated here themselves, are the least likely to agree with Trump. Third generation congressprople are the most likely to agree with Trump.

I would like to be able to predict how likely it is for congresspeople whos families have been living in the country for several or multiple generations. The above graph gives an idea of the trend.


Modeling
```{r}
cor(as.numeric(averages$generation), averages$agree_pct)
model <- lm(averages$agree_pct ~ as.numeric(averages$generation) + averages$predicted_agree)
summary(model)
plot(model)
```


```{r}
set.seed(333)

index <- createDataPartition(averages$agree_pct, p = 0.75, list = FALSE)

train <- averages[index, ]
test <- averages[index, ]

trained_model <- lm(train, formula = agree_pct~predicted_agree+generation)
summary(trained_model)


generation_agree_predictions <- predict(trained_model, test)
ggplot(data=test, aes(generation_agree_predictions, generation)) + geom_point(color='purple') + xlab('generation agree predictions')
```
Here we are creating a test and training set and using that to predict the likelyhood of a politician to agree with Trump based on what generation they are. I'm not surprised by this data but I think it is still very interesting to see it graphed out. You could definitely use this data to predict how likely a politician is to vote with Trump. 